\documentclass[11pt]{article}

\input{Shared.tex}

\parindent0in
\pagestyle{plain}
\thispagestyle{plain}

\usepackage{csquotes}
\usepackage[shortlabels]{enumitem}

\newcommand{\dated}{\today}
\newcommand{\token}[1]{\langle \text{#1} \rangle}

\begin{document}

\textbf{Introduction to the Theory of
Computation}\hfill\textbf{\myname}\\[0.01in]
\textbf{Chapter 5: Reducibility}\hfill\textbf{\dated}\\
\smallskip\hrule\bigskip

\begin{problem}{5.26}
Define a \textbf{\textit{two-headed finite automaton}} (2DFA) to be a deterministic finite automaton that has two read-only, bidirectional heads that start at the left-hand end of the input tape and can be independently controlled to move in either direction. The tape of a 2DFA is finite and is just large enough to contain the input plus two additional blank tape cells, one on the left-hand end and one on the right-hand end, that serve as delimiters. A 2DFA accepts its input by entering a special accept state. For example, a 2DFA can recognize the language ${a^nb^nc^n \ | \ n \geq 0}$.
\end{problem}

\begin{problem}[Part]{a}
Let $A_{2DFA} = \{\langle M, x \rangle \ | \ M \text{ is a 2DFA and } M \text{ accepts } x\}$. Show that $A_{2DFA}$ is decidable.
\end{problem}

\begin{proof}
First, we define a notation for representing different configurations of a 2DFA, and then we calculate the number of distinct configurations of a 2DFA for an input of length $n$. \\

For a state $q$ and two strings $u$ and $v$ over the input alphabet $\Sigma$, we write $q \sqcup \circ \ u \bullet v \ \sqcup$ for the configuration  where the current state is $q$, the current input is $uv$, the current first and second head locations are the first symbols of $u$ and $v$ respectively. For a 2DFA with $q$ states, there are exactly $q(n + 2)^2$ distinct configurations for an input of length $n$. Construct decider $S$ for $A_{2DFA}$ as follows. \\

$S =$ \textquotedblleft On input $\langle M, x \rangle$, where $M$ is a 2DFA and $x$ is a string:
\begin{enumerate}
\item Let $n$ be the length of string $x$.
\item Simulate $M$ on $x$ for $q(n + 2)^2$ steps or until it halts.
\item If $M$ has halted, \textit{accept} if it has accepted and \textit{reject} if it has rejected. If it has not halted, \textit{reject}.\textquotedblright
\end{enumerate}
\end{proof}

\begin{problem}[Part]{a}
Let $E_{2DFA} = \{\langle M \rangle \ | \ M \text{ is a 2DFA and } L(M) = \emptyset   \}$. Show that $E_{2DFA}$ is not decidable.
\end{problem}

\begin{proof}
\end{proof}

\end{document}